BOAST: a Metaprogramming Framework to Produce Portable and Efficient Computing Kernels for HPC Applications

### 2014-09-09 Paper/BOAST.tex
Refactoring

\lstdefinestyle{BOAST}{
  language=Ruby, 
  basicstyle=\scriptsize, 
  backgroundcolor=\color{white}, 
  frame=single, 
  captionpos=b,
  morekeywords={BOAST, print, decl, open, close}
}

@@

In order to clearly differentiate what is going to be generated from what is
related to manipulations in the host language four keywords were defined. They
are \emph{print}, \emph{decl}, \emph{open} and \emph{close}. As the language is
an EDSL, these four keywords are methods in the BOAST namespace.

The \emph{print} method calls the public \emph{print} method of Objects it is
called on. Each BOAST object is responsible for printing itself correctly
depending on the BOAST configuration at the time the print public method is
called. Calling directly the print method of a BOAST object yields the same
result.

@@

\begin{figure}
\lstset{style=BOAST,
        caption={BOAST code}, 
        label={lst:BOAST_algebra} }
\begin{lstlisting}
i = BOAST::Int("i") # or BOAST::Variable::new(Int, "i")
k = BOAST::Int("k", :size => 8)
l = BOAST::Real("l", :dim => [ BOAST::Dim(-5, 20) ], :local => true )
BOAST::decl i, k, l
BOAST::print i === 5
j = i + 5
BOAST::print k === j * 2
BOAST::print l[k] === 1.0
BOAST::print l[k-1] === BOAST::sin(l[k])
\end{lstlisting}

@@

Figure~\ref{fig:BOAST_algebra} shows some basic usage of both Variables and
Expressions as well as the \emph{print} and \emph{decl} keywords. For clarity we
stayed out of BOAST namespace so BOAST related class and methods are prefixed
with \emph{BOAST::}. Listing~\ref{lst:BOAST_algebra} shows the BOAST code that
when run produces the FORTRAN (Listing~\ref{lst:BOAST_algebra_FORTRAN}) and C
(Listing~\ref{lst:BOAST_algebra_C}) output. On the last line, a call to the
\emph{sin} function is made through the automatic creation of a FuncCall object.
This automatic behaviors is limited to BOAST namespace, and thus, here, the
function call has to be prefixed with \emph{BOAST::}.

>>>>

\lstdefinestyle{BOAST}{
  language=Ruby, 
  basicstyle=\scriptsize, 
  backgroundcolor=\color{white}, 
  frame=single, 
  captionpos=b,
  morekeywords={BOAST, pr, decl, open, close}
}

@@

In order to clearly differentiate what is going to be generated from what is
related to manipulations in the host language four keywords were defined. They
are \emph{pr}, \emph{decl}, \emph{open} and \emph{close}. As the language is
an EDSL, these four keywords are methods in the BOAST namespace.

The \emph{pr} method calls the public \emph{pr} method of Objects it is
called on. Each BOAST object is responsible for printing itself correctly
depending on the BOAST configuration at the time the print public method is
called. Calling directly the print method of a BOAST object yields the same
result.

@@

\begin{figure}
\lstset{style=BOAST,
        caption={BOAST code}, 
        label={lst:BOAST_algebra} }
\begin{lstlisting}
i = BOAST::Int("i") # or BOAST::Variable::new(Int, "i")
k = BOAST::Int("k", :size => 8)
l = BOAST::Real("l", :dim => [ BOAST::Dim(-5, 20) ], :local => true )
BOAST::decl i, k, l
BOAST::pr i === 5
j = i + 5
BOAST::pr k === j * 2
BOAST::pr l[k] === 1.0
BOAST::pr l[k-1] === BOAST::sin(l[k])
\end{lstlisting}

@@

Figure~\ref{fig:BOAST_algebra} shows some basic usage of both Variables and
Expressions as well as the \emph{pr} and \emph{decl} keywords. For clarity we
stayed out of BOAST namespace so BOAST related class and methods are prefixed
with \emph{BOAST::}. Listing~\ref{lst:BOAST_algebra} shows the BOAST code that
when run produces the FORTRAN (Listing~\ref{lst:BOAST_algebra_FORTRAN}) and C
(Listing~\ref{lst:BOAST_algebra_C}) output. On the last line, a call to the
\emph{sin} function is made through the automatic creation of a FuncCall object.
This automatic behaviors is limited to BOAST namespace, and thus, here, the
function call has to be prefixed with \emph{BOAST::}.
